Scale Space Edge Detection

### 2018-03-05 paper.tex
Fix listings specification

    % Define the coloring for keywords in Julia
    \lstdefinelanguage{Julia}%
    {morekeywords={abstract,break,case,catch,const,continue,do,else,elseif,%
        end,export,false,for,function,immutable,import,importall,if,in,%
        macro,module,otherwise,quote,return,switch,true,try,type,typealias,%
        using,while},%
        sensitive=true,%
        alsoother={$},%
        morecomment=[l]\#,%
        morecomment=[n]{\#=}{=\#},%
        morestring=[s]{"}{"},%
        morestring=[m]{'}{'},%
    }[keywords,comments,strings]%

>>>>

% Define the coloring for keywords in Julia
\lstdefinelanguage{Julia}%
{morekeywords={abstract,break,case,catch,const,continue,do,else,elseif,%
    end,export,false,for,function,immutable,import,importall,if,in,%
    macro,module,otherwise,quote,return,switch,true,try,type,typealias,%
    using,while},%
  sensitive=true,%
  morecomment=[l]\#,%
  morecomment=[n]{\#=}{=\#},%
  morestring=[s]{"}{"},%
  morestring=[m]{'}{'},%
}[keywords,comments,strings]%
